\chapwithtoc{List of Attached Files}
\label{chap:files}

This is a list of files attached to this work. Source code is also available online, see appendices~\ref{chap:map_merge-doc}~\ref{chap:explore-doc}.

\medskip
\dirtree{%
.1 attachements.zip. %
.2 merging-with-known-initial-positions\DTcomment{experiment data, see~\ref{sec:merging-with-known-initial-positions}}. %
.2 minimal-overlapping-area\DTcomment{experiment data, see~\ref{sec:minimal-overlaping-area}}. %
.2 retaining-largest-transformation\DTcomment{experiment data, see~\ref{sec:retaining-largest-transformation}}. %
.2 probability-model-evaluation\DTcomment{experiment data, see~\ref{sec:probability-model-evaluation}}. %
.2 m-explore\DTcomment{source code for ROS packages, see~\ref{chap:ros-packages}}. %
.3 explore\DTcomment{see~\ref{sec:explore_lite-package}}. %
.4 doc\DTcomment{package and code documentation}. %
.4 include. %
.5 explore. %
.6 explore.h\DTcomment{ROS node}. %
.6 navfn\_ros.h\DTcomment{ROS planner with extended API, see~\ref{sec:frontier-search}}. %
.6 explore\_frontier.h\DTcomment{see~\ref{sec:frontier-search}}. %
.6 costmap\_client.h\DTcomment{see~\ref{sec:map-sourcing}}. %
.4 launch. %
.4 src. %
.3 map\_merge\DTcomment{see~\ref{sec:map_merge-package}}. %
.4 doc\DTcomment{package and code documentation}. %
.4 test\DTcomment{gtest based tests}. %
.4 include. %
.5 combine\_grids\DTcomment{implements algorithm presented in section~\ref{chap:mergingalgorithm}}. %
.5 occupancy\_grid\_utils\DTcomment{see~\ref{sec:map-composition}}. %
.5 map\_merge. %
.6 map\_merge.h\DTcomment{ROS node}. %
.4 launch. %
.4 src. %
}
